---
title: 'Tidymodels: tidy machine learning in R'
date : "10 May 2021"
output: html_document
---

- reference : [Tidymodels: tidy machine learning in R](http://www.rebeccabarter.com/blog/2020-03-25_machine_learning/)

## Getting set up
```{r}
suppressMessages(library(magrittr))
suppressMessages(library(tidymodels)) %>% suppressWarnings()
suppressMessages(library(tidyverse)) %>% suppressWarnings()
suppressMessages(library(skimr)) %>% suppressWarnings()
suppressMessages(library(knitr)) %>% suppressWarnings()

library('mlbench')
```

```{r}
data("PimaIndiansDiabetes")
diabetes_orig <- PimaIndiansDiabetes

diabetes_orig %>% head()
```
```{r}
diabetes_clean<- diabetes_orig %>% mutate_at(vars(triceps, glucose, pressure, insulin, mass),
                            function(.var){
                              if_else(condition = (.var == 0),
                                      true = as.numeric(NA),
                                      false = .var)
                            })
```



## Split into train / test
```{r}
set.seed(1234)
diabetes_split <- initial_split(diabetes_clean, 
                                prop = 3/4)
```

```{r}
# extract training and testing sets
diabetes_train <- training(diabetes_split)
diabetes_test <- testing(diabetes_split)
```

```{r}
# create CV object from training data
diabetes_cv <- vfold_cv(diabetes_train, v = 5)

```

## Define a recipe
```{r}
diabetes_recipe <- recipe(diabetes ~ ., data  = diabetes_clean) %>% 
  step_normalize(all_numeric()) %>% 
  step_knnimpute(all_predictors())
  
diabetes_recipe
```

```{r}
diabetes_train_preprocessed <- diabetes_recipe %>% 
  prep(training = diabetes_train) %>% 
  juice()

diabetes_train_preprocessed %>% head()
```

## Specify the model
```{r}
rf_model <- 
  # specify that the model is a random forest
  rand_forest() %>% 
  # specify that the `mtry` parameter needs to be tuned\
  set_args(mtry = tune(), trees = tune()) %>% 
  # select the engine/package that underlies the model
  set_engine("ranger", importance =  "impurity") %>%  # importance = impurity or permutation
  # choose either the continuous regression or binary classification mode
  set_mode("classification")
```

```{r}
lr_model <-
  # specify that the model is a logistic regression
  logistic_reg() %>% 
  # select the engine/package that underlines the model
  set_engine("glm") %>% 
  set_mode("classification")
```

## Put it all together in a workflow

```{r}
rf_workflow <- workflow() %>% 
  # add the recipe
  add_recipe(diabetes_recipe) %>% 
  # add the model
  add_model(rf_model)
```

## Tune the parameters
```{r}
# specify which values eant to try
rf_grid <- expand.grid(mtry = c(3,4,5), trees = c(100, 500))

# extract results
rf_tune_results <- rf_workflow %>% 
  tune_grid(resamples = diabetes_cv, #CV object
            grid = rf_grid, # grid of values to try
            metrics = metric_set(accuracy, roc_auc) # metrics we care about
            )
```

```{r}
rf_tune_results %>% 
  collect_metrics() %>% arrange(desc(mean))
```

## Finalize the workflow
```{r}
param_final <- rf_tune_results %>% 
  select_best(metric = 'roc_auc')
  
param_final
```
- add the parameters to the workflow
```{r}
rf_workflow <- rf_workflow %>% 
  finalize_workflow(param_final)
```

## Evaluate the model on the test set
- `last_fit` 함수에서는 자동으로 train data set으로 workflow을 구축하고 test set으로 평가를 한다.
```{r}
rf_fit <- rf_workflow %>% 
  # fit on the training set and evaluate on test set
  last_fit(diabetes_split)
```

```{r}
rf_fit
```

```{r}
rf_fit %>% collect_metrics()
```

```{r}
# generate predictions from the test set
test_predictions <- rf_fit %>% collect_predictions()
#test_predictions <- rf_fit %>% pull(.predictions)

test_predictions

```


## Fitting and using your final model
```{r}
final_model <- fit(rf_workflow, diabetes_clean)
```

```{r}
final_model
```

```{r}
new_woman <- tribble(~pregnant, ~glucose, ~pressure, ~triceps, ~insulin, ~mass, ~pedigree, ~age,
                     2, 95, 70, 31, 102, 28.2, 0.67, 47)

new_woman
```

```{r}
predict(final_model, new_data = new_woman)
```

## Variable importance
```{r}
ranger_obj <- pull_workflow_fit(final_model)$fit
ranger_obj
```

```{r}
ranger_obj$variable.importance
```

